Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-14 PAPER.tex
Removed "small injection" discussion now irrelevant with Pout=Pr interpretation.  Added sentence about model for cross term

{\bf Small injection:}
In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$. They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected. This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. In this regime, we also note that the cross-terms (red) behave as noise, even in the empirically inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below)%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term. However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$. It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black). We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).

>>>>

{\bf Small injection:}
%In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$. They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected. 
%This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. 
In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples. Output values are gaussian distributed around zero, spanning a range of values set by the injection level. This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below). In fact, for the unweighted case, the cross term is well modeled by $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}=\sqrt{p_e}\sqrt{p_x}$ %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term. However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$. It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black). We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
